---
title: "Contact information"
header-includes:
  - \usepackage{fontawesome}
---

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-right{
  float: right;
  width: 50%;
  text-align: right;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(fontawesome)
library(png)
```

<div class="column-left">
<p>
<i class="fas fa-map-marker-alt fa-1x" style="color:dodgerblue"></i> [L'Institut Agro Rennes Angers](https://www.institut-agro-rennes-angers.fr/)
 
Département Statistique et Informatique
 
65 rue de Saint-Brieuc CS 84215

35042 Rennes cedex, FRANCE

&nbsp;

<i class="fas fa-envelope fa-1x" style="color:dodgerblue"></i> david [dot] causeur [at] institut-agro [dot] fr 
 
&nbsp;

<i class="fas fa-phone fa-1x" style="color:dodgerblue"></i> +33 (0) 223 485 884

&nbsp; 

 `r fa("researchgate", fill = "dodgerblue", height = "1em")` [Researchgate](https://www.researchgate.net/profile/David-Causeur)
 
&nbsp;

 `r fa("google", fill = "dodgerblue", height = "1em")` [Google scholar](https://scholar.google.com/citations?user=kCws61IAAAAJ&hl=fr)

&nbsp;

 `r fa("github", fill = "dodgerblue", height = "1em")` [Github](https://github.com/dcauseur)
</p>
</div>

<div class="column-right">
```{r echo = FALSE, fig.width=5, fig.height=3.1}
img <- readPNG("./img/profile.png")
grid::grid.raster(img)
```
</div>
